Probability

### 2016-04-21 prob.tex
prob.tex Change variable name from A to E in order to: 1. Clearly express that E is an event; 2. Avoid confusing with the whole *-algebra in the literature, bucause we are not using the full algebra...

\theoremstyle{remark}
\newtheorem{example}{Example}
\newcommand{\events}{\ensuremath{\mathcal{A}}}
\newcommand{\qevents}{\ensuremath{\mathcal{A}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}\in\Hilb$ induces
a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
space of events defined for any event $A\in\qevents$ as follows:
\[
\mu_\psi(A) = \ip{\psi}{A\psi}
\]
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $A_i$, we have
  $\mu(\sum_i A_i) = \sum_i \mu(A_i)$.

>>>>

\theoremstyle{remark}
\newtheorem{example}{Example}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}

@@

We now formalize a \emph{quantum probability space} as
follows~\cite{Maassen2010,Swart2013}. We first assume an ambient
Hilbert space~$\Hilb$ and define the set of events $\qevents$ as all
\emph{projections} on~$\Hilb$. Each quantum state $\ket{\psi}\in\Hilb$ induces
a probability measure $\mu_\psi : \qevents \rightarrow [0,1]$ on the
space of events defined for any event $E\in\qevents$ as follows:
\[
\mu_\psi(E) = \ip{\psi}{E\psi}
\]
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$.
